### 2011-05-06 paper/paper.tex
edited conclusion

In conclusion, we have found that the results of our tests confirm what we thought to be theoretically true: the hit-and-run method performs much better than the Metropolis methods. With a good start, hit-and-run required only something on the order of $1000$ iterations to produce a distribution that seemed reasonably uniform, which is even better than the bound given in Theorem \ref{hitandrunbound}, even with $100$ dimensions, whereas this cube is too larger for the the basic-ball walking method to have a good chance of even reaching the edges. We also saw that the basic Gaussian-walking method worked better than the ball-walking method in this case.

@@

These results indicate that, in practice, the hit-and-run method is better than the Metropolis methods, even when taking into account its slower transition step. Among the Metropolis methods, the Gaussian-walking method is a slight improvement over the ball-walking method, and the adaptive methods usually help in cases where are starting point is near a corner.

>>>>

In conclusion, we have found that the results of our tests confirm what we thought to be theoretically true: the hit-and-run method performs much better than the Metropolis methods. With a good start, hit-and-run required only something on the order of $1000$ iterations to produce a distribution that seemed reasonably uniform, which is even better than the bound given in Theorem \ref{hitandrunbound}, even with $100$ dimensions, whereas this cube is too large for the the basic-ball walking method to have a good chance of even reaching the edges. We also saw that the basic Gaussian-walking method worked better than the ball-walking method in this case.

@@

These results indicate that, in practice, the hit-and-run method is better than the Metropolis methods, even when taking into account its slower transition step. Among the Metropolis methods, the Gaussian-walking method is a slight improvement over the ball-walking method. While the adaptive method does not seem to help for the Gaussian method, we find that it does provide an improvement for the ball-walking method when starting in a corner.
